Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-08-03 analysis/paper/Rmd/hotspots-paper.Rmd
added dryad citation

```{r setup_continued}
hot_chr <- c(2, 5, 7, 11, 13)
hot_mid <- c(165.5, 146, 46, 71, 112.5)
keller_mediator <- c("Hnf4a", "Pdx1", "Fam83e", "Sat2", "Il6st")
inputs <- tibble(hot_chr, hot_mid, keller_mediator)
out <- pmap_dfc(inputs, .f = function(hot_chr, hot_mid, keller_mediator) knitr::knit_expand(text = readLines(here::here("analysis", "paper", "hotspot-one-chromosome.Rmd"))))
# note that ... argument must be a list, ie, it must be a single argument, not multiple args
```

>>>>

```{r setup_continued}
hot_chr <- c(2, 5, 7, 11, 13)
hot_mid <- c(165.5, 146, 46, 71, 112.5)
keller_mediator <- c("Hnf4a", "Pdx1", "Fam83e", "Sat2", "Il6st")
inputs <- tibble(hot_chr, hot_mid, keller_mediator)
out <- pmap_dfc(inputs, .f = function(hot_chr, hot_mid, keller_mediator) knitr::knit_expand(text = readLines(here::here("analysis", "paper", "Rmd", "hotspot-one-chromosome.Rmd"))))
# note that ... argument must be a list, ie, it must be a single argument, not multiple args
```

### 2019-08-03 analysis/paper/Rmd/methods.Rmd
organized analysis/paper dir
added dryad citation

We used the publicly available data from @keller2018genetic to demonstrate our strategy. @keller2018genetic
measured genome-wide gene expression levels with RNA sequencing of pancreatic islets in 378 Diversity Outbred mice. From the RNA sequencing counts, they obtained normalized gene expression levels for 21,771 transcripts, which they shared publicly via DataDryad ().

>>>>

We used the publicly available data from @keller2018genetic to demonstrate our strategy. @keller2018genetic
measured genome-wide gene expression levels with RNA sequencing of pancreatic islets in 378 Diversity Outbred mice. From the RNA sequencing counts, they obtained normalized gene expression levels for 21,771 transcripts, which they shared publicly via DataDryad [@dryad]. @keller2018genetic also included founder allele probabilities at 69,005 markers across the genome, covariates, and leave-one-chromosome-out estimated kinship matrices. @keller2018genetic calculated leave-one-chromosome-out kinship matrices for every chromosome [@broman2019rqtl2; @yang2014advantages].
